---
title: "Comparison of Ensemble Recalibration Methods in Flu Forecasting 2"
author: "Nutcha Wattanachit"
date: "02/15/2021"
header-includes:
   - \usepackage{booktabs}
   - \usepackage{tabularx}
   - \usepackage{amssymb}
   - \usepackage{hyperref}
   - \usepackage{multicol}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage{makecell}
   - \usepackage{xcolor}
output:
  pdf_document:
        keep_tex: true
        latex_engine: xelatex
        extra_dependencies: ["float"]
---

```{r setup, include=FALSE}
library(Matrix)
library(tidyverse)
library(tidyr)
library(mixtools)
library(knitr)
library(rstan)

knitr::opts_chunk$set(echo = FALSE, 
                      #warning(file = "./R-warnings.txt"),
                      comment = FALSE, message=FALSE, fig.show= 'hold', fig.pos="h",
                      table.placement='h')
#options(kableExtra.latex.load_packages = FALSE)
```

# Simulation study with empirical distributions

This markdown doesn't include BLP, EW-BLP since these can be done not using stan. It also doesn't include any EW-BMC since it will work if BMC works. 

```{r, include=FALSE}
set.seed(1234)
source("./applied_blp_sim_ver2.R")
# -----------Scenario 0: Simulation setup -----------------------#
n <- 2000
forecast_names <- c("TLP", "BLP","EW", "EW-BLP",
                    "BMC2","EW-BMC2","BMC3","EW-BMC3",
                    "BMC4","EW-BMC4","BMC5","EW-BMC5")
ind_est <- sample(1:n,n-(n/5))
```


## Scenario 2: Multimodal DGP (Normal mixture) with empirical distributions

This is the same scenario as in the other markdown. The data generating process for the observation $y_t$ is 

$$
y_t \overset{i.i.d.}{\sim} p_1\text{N}(-2,0.25)+p_2\text{N}(0,0.25)+p_3\text{N}(2,0.25), \\
t= 1,...,1000
$$

where $p_1=0.2,p_2=0.2$, and $p_3=0.6$. However, here we will simulate from the normal distributions to make empirical pdfs. Since we calculate the binned probability exactly from normal distributions, binned probabilities (empirical pdfs) are exactly the same for all $t$ in each component model.

```{r, include=FALSE}
# data simulation
p <- c(0.2,0.2,0.6)
mu <- c(-2,0,2)
sigma <- rep(0.25, 3)
Y <- data.frame(cbind(index=1:n,Y=rnormmix(n, p, mu, sigma)))
# build component model
## set bins
bin_start <- c(-Inf,seq(-3,3,0.25^2))
bin_end <- c(dplyr::lead(bin_start)[-length(bin_start)],Inf)
index <- c()
for(i in 1:n){
  index <- c(index,rep(i,length(bin_start)))
}
temp <- data.frame(cbind(index,rep(bin_start,n),rep(bin_end,n)))
names(temp)[2:3] <- c("bin_start","bin_end")
rm(bin_start,bin_end,index)
#  fill in bin probs
comp_names <- c("binned_forecast1","binned_forecast2","binned_forecast3")
comp_binned_forecasts <- data.frame()
for(j in 1:length(comp_names)){
  frame <- temp %>%
    dplyr::group_by(index) %>%
    dplyr::mutate(binned_probs=pnorm(bin_end,mu[j],sigma) - pnorm(bin_start,mu[j],sigma),
                  model=comp_names[j]) %>%
    ungroup()
  rbind(comp_binned_forecasts,frame) -> comp_binned_forecasts
}
rm(temp,frame)
```

The individual predictive densities are defined as follows:

$$
\begin{aligned}
f_{1}&\overset{i.i.d.}{\sim}\text{N}(-2,0.25)\\
f_{2}&\overset{i.i.d.}{\sim}\text{N}(0,0.25)\\
f_{3}&\overset{i.i.d.}{\sim}\text{N}(2,0.25)\\
\end{aligned}
$$


```{r, include=FALSE}
M <- length(unique(comp_binned_forecasts$model))
# get ensemble params
# TLP/BLP/EW/EW-BLP -----------------------------------
EW_params <- rep(1/M,M)
TLP_params <- make_ensemble("TLP", K=1, M=M, ind_est, Y, comp_binned_forecasts,
                            initial_vals=list(omega=EW_params),
                            hyperpars=NULL)

# make initial values
EWBLP_init <- list(alpha=rnorm(1,1,1e-3), beta=rnorm(1,1,1e-3), w=1.0)
dim(EWBLP_init$alpha) <- 1
dim(EWBLP_init$beta) <- 1
dim(EWBLP_init$w) <- 1
BLP_init <- c(EWBLP_init,list(omega_k=TLP_params))
dim(BLP_init$omega_k) <- c(1,3)

# run 
BLP_params <- make_ensemble("BLP", K=1,M=M, ind_est, Y, comp_binned_forecasts,
                            initial_vals=BLP_init,
                            hyperpars=NULL)
EW_BLP_params <- make_ensemble("EW-BLP", K=1,M=M, ind_est, Y, comp_binned_forecasts,
                               initial_vals=EWBLP_init, 
                               hyperpars=NULL)

# experimental vanilla mixture
#for(i in 2:5){
for(i in 4:5){
  K<- i
  w_vec_inits <- sample.int(100, size = K, replace = FALSE)
  init_vals_ew <- list(alpha=rnorm(K,1,1e-3),beta=rnorm(K,1,1e-3),w=w_vec_inits/sum(w_vec_inits))
  init_vals <- c(init_vals_ew, omega_k=t(replicate(K, TLP_params)))
  hyperpars <- list(alpha_w=rep(1.0,K),alpha_omega=rep(1.0,M))
  assign(paste0("BM",i,"_params"),
         make_ensemble("BLP", K=K,M=M, ind_est, Y, comp_binned_forecasts,
                       initial_vals=init_vals,hyperpars=NULL)
         )
  assign(paste0("EW_BM",i,"_params"),
         make_ensemble("EW-BLP", K=K,M=M, ind_est, Y, comp_binned_forecasts,
                       initial_vals=init_vals_ew,hyperpars=NULL)
         )
}


# # BMC/EW-BMC --------------------------------------------------------------------------
# for(mix_ens in forecast_names[5:12]){
#   K<- as.numeric(substring(mix_ens,nchar(mix_ens)))
#   w_vec_inits <- sample.int(100, size = K, replace = FALSE)
#   init_vals <- list(mu=rnorm(K,0.5,1e-3),nu=rnorm(K,2,1e-3),w=w_vec_inits/sum(w_vec_inits))
#   if(!(grepl(mix_ens,"EW",fixed = TRUE))){
#     init_vals[["omega_k"]] <- t(replicate(K, TLP_params))
#     } 
#   hyperpars <- list(alpha_w=rep(1.0,K),alpha_omega=rep(1.0,M))
#   assign(paste0(mix_ens,"_params"),
#          make_ensemble(mix_ens, K=K,M=M, ind_est, Y, comp_binned_forecasts,
#                        initial_vals=init_vals,hyperpars=hyperpars)
#          )
# }

# params_list <- list(BLP_params, EW_BLP_params, BMC2_params, BMC3_params, BMC4_params,BMC5_params,
#                     `EW-BMC2_params`, `EW-BMC3_params`, `EW-BMC4_params`, `EW-BMC5_params`)
# save(params_list, file="./Renvir/run2.RData")
```

```{r, include=FALSE}
# Evaluation ------------------------------------------------------------------
# get component results
for(i in 1:M){
  assign(paste0(comp_names[i],"_results"), 
         comp_binned_forecasts %>%
           dplyr::filter(model==comp_names[i]) %>%
           dplyr::select(-"model") %>%
           ls_pit_calc(., Y, ind_est))
}

#### add ensemble results once we get the parameters
```