---
title: "Comparison of Ensemble Recalibration Methods in Flu Forecasting 2"
author: "Nutcha Wattanachit"
date: "02/03/2021"
header-includes:
   - \usepackage{booktabs}
   - \usepackage{tabularx}
   - \usepackage{amssymb}
   - \usepackage{hyperref}
   - \usepackage{multicol}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage{makecell}
   - \usepackage{xcolor}
output:
  pdf_document:
        keep_tex: true
        latex_engine: xelatex
        extra_dependencies: ["float"]
---

```{r setup, include=FALSE}
library(Matrix)
library(tidyverse)
library(tidyr)
library(mixtools)
library(knitr)
library(rstan)

knitr::opts_chunk$set(echo = FALSE, 
                      #warning(file = "./R-warnings.txt"),
                      comment = FALSE, message=FALSE, fig.show= 'hold', fig.pos="h",
                      table.placement='h')
#options(kableExtra.latex.load_packages = FALSE)
```

# Simulation study with empirical distributions

```{r, include=FALSE}
set.seed(1234)
source("./applied_blp_sim_ver2.R")
# -----------Scenario 0: Simulation setup -----------------------#
n <- 5000
forecast_names <- c("TLP", "BLP","EW", "EW-BLP",
                    "BMC2","EW-BMC2","BMC3","EW-BMC3",
                    "BMC4","EW-BMC4","BMC5","EW-BMC5")
ind_est <- sample(1:n,n-(n/5))
```


## Scenario 2: Multimodal DGP (Normal mixture) with empirical distributions

This is the same scenario as in the other markdown. The data generating process for the observation $y_t$ is 

$$
y_t \overset{i.i.d.}{\sim} p_1\text{N}(-2,0.25)+p_2\text{N}(0,0.25)+p_3\text{N}(2,0.25), \\
t= 1,...,5000
$$

where $p_1=0.2,p_2=0.2$, and $p_3=0.6$. However, here we will simulate from the normal distributions to make empirical pdfs.

```{r, include=FALSE}
# data simulation
p <- c(0.2,0.2,0.6)
mu <- c(-2,0,2)
sigma <- rep(0.25, 3)
Y <- data.frame(cbind(index=1:n,Y=rnormmix(n, p, mu, sigma)))
# build component model
## set bins
bin_start <- c(-Inf,seq(-3,3,0.25^2))
bin_end <- c(dplyr::lead(bin_start)[-length(bin_start)],Inf)
index <- c()
for(i in 1:n){
  index <- c(index,rep(i,length(bin_start)))
}
temp <- data.frame(cbind(index,rep(bin_start,n),rep(bin_end,n)))
names(temp)[2:3] <- c("bin_start","bin_end")
rm(bin_start,bin_end,index)
#  fill in bin probs
comp_names <- c("binned_forecast1","binned_forecast2","binned_forecast3")
comp_binned_forecasts <- data.frame()
for(j in 1:length(comp_names)){
  frame <- temp %>%
    dplyr::group_by(index) %>%
    dplyr::mutate(binned_probs=pnorm(bin_end,mu[j],sigma) - pnorm(bin_start,mu[j],sigma),
                  model=comp_names[j]) %>%
    ungroup()
  rbind(comp_binned_forecasts,frame) -> comp_binned_forecasts
}
rm(temp,frame)
```

The individual predictive densities are defined as follows:

$$
\begin{aligned}
f_{1}&\overset{i.i.d.}{\sim}\text{N}(-2,0.25)\\
f_{2}&\overset{i.i.d.}{\sim}\text{N}(0,0.25)\\
f_{3}&\overset{i.i.d.}{\sim}\text{N}(2,0.25)\\
\end{aligned}
$$


```{r, include=FALSE}
M <- length(unique(comp_binned_forecasts$model))
# make density forecasts and component PITs
# get component results
for(i in 1:M){
  assign(paste0(comp_names[i],"_results"), 
         comp_binned_forecasts %>%
           dplyr::filter(model==comp_names[i]) %>%
           dplyr::select(-"model") %>%
           ls_pit_calc(., Y, ind_est))
}
# get ensemble params
# TLP/BLP/EW/EW-BLP -----------------------------------
EW_params <- rep(1/M,M)
# make init for sampling
# initf1 <- function(chain_id = 1) {
#   # cat("chain_id =", chain_id, "\n")
#   c(list(omega=EW_params),list(alpha = chain_id))
# }
# generate a list of lists to specify initial values
# n_chains <- 4
# init_tlp <- lapply(1:n_chains, function(id) initf1(chain_id = id))
TLP_params <- make_ensemble("TLP", K=1, M=M, ind_est, Y, comp_binned_forecasts,
                            initial_vals=list(omega=EW_params),
                            hyperpars=NULL)
# make initial values
#EWBLP_init <- list(mu=rnorm(1,0.5,1e-3), nu=rnorm(1,2.0,1e-3), w=1.0)
EWBLP_init <- list(alpha=rnorm(1,1,1e-3), beta=rnorm(1,1,1e-3))

dim(EWBLP_init$alpha) <- 1
dim(EWBLP_init$beta) <- 1
# dim(EWBLP_init$w) <- 1
BLP_init <- c(EWBLP_init,list(omega_k=TLP_params))
dim(BLP_init$omega_k) <- c(1,3)
# # create list of list for sampling
# initf2 <- function(chain_id = 1) {
#   # cat("chain_id =", chain_id, "\n")
#   c(BLP_init,list(alpha = chain_id))
# }
# # generate a list of lists to specify initial values
# n_chains <- 4
# init_ll <- lapply(1:n_chains, function(id) initf2(chain_id = id))
source("./applied_blp_sim_ver2.R")

# run 
BLP_params <- make_ensemble2("BLP", K=1,M=M, ind_est, Y, comp_binned_forecasts,
                            initial_vals=BLP_init,
                            # initial_vals=init_ll,
                            hyperpars=NULL)

EW_BLP_params <- make_ensemble2("EW-BLP", K=1,M=M, ind_est, Y, comp_binned_forecasts,
                               initial_vals=EWBLP_init,
                               hyperpars=NULL)

# BMC/EW-BMC --------------------------------------------------------------------------
#for(mix_ens in forecast_names[5:12]){
for(mix_ens in forecast_names[5]){
  if(grepl(2,mix_ens, fixed = TRUE)){
    K<-2
    init_vals <- list(mu=rnorm(2,0.5,1e-3),nu=rnorm(2,2,1e-3),w=c(0.3,0.7))
    } else if(grepl(3,mix_ens, fixed = TRUE)){
      K<-3
      init_vals <- list(mu=rnorm(3,0.5,1e-3),nu=rnorm(3,2,1e-3),w=c(0.1,0.3,0.6))
      } else if(grepl(4,mix_ens, fixed = TRUE)){
        K<-4
        init_vals <- list(mu=rnorm(4,0.5,1e-3),nu=rnorm(4,2,1e-3),w=c(0.1,0.3,0.4,0.2))
      } else if(grepl(5,mix_ens, fixed = TRUE)){
        K<-5
        init_vals <- list(mu=rnorm(5,0.5,1e-3),nu=rnorm(5,2,1e-3),w=c(0.1,0.2,0.3,0.35,0.05))
      } 
  if(!(grepl(mix_ens,"EW",fixed = TRUE))){
    init_vals[["omega_k"]] <- t(replicate(K, TLP_params))
    } 
  hyperpars <- list(rep(1.0,K),rep(1.0,M),rep(1/M,M))
  names(hyperpars) <- c("alpha_w","alpha_omega","omega_ew")
  assign(paste0(mix_ens,"_params"),
         make_ensemble(mix_ens, K=K,M=M, ind_est, Y, comp_binned_forecasts,
                       initial_vals=init_vals,hyperpars=hyperpars)
         )
  }
# for(mix_ens in forecast_names[5:12]){
#   if(grepl(2,mix_ens, fixed = TRUE)){
#     K<-2
#     init_vals <- list(mu=rnorm(2,0.5,1e-3),nu=rnorm(2,2,1e-3),w=c(0.3,0.7))
#     } else if(grepl(3,mix_ens, fixed = TRUE)){
#       K<-3
#       init_vals <- list(mu=rnorm(3,0.5,1e-3),nu=rnorm(3,2,1e-3),w=c(0.1,0.3,0.6))
#       } else if(grepl(4,mix_ens, fixed = TRUE)){
#         K<-4
#         init_vals <- list(mu=rnorm(4,0.5,1e-3),nu=rnorm(4,2,1e-3),w=c(0.1,0.3,0.4,0.2))
#       } else if(grepl(5,mix_ens, fixed = TRUE)){
#         K<-5
#         init_vals <- list(mu=rnorm(5,0.5,1e-3),nu=rnorm(5,2,1e-3),w=c(0.1,0.2,0.3,0.35,0.05))
#       } else if(grepl(1,mix_ens, fixed = TRUE)){
#         K<-1
#         init_vals <- list(mu=rnorm(1,0.5,1e-3),nu=rnorm(1,2,1e-3),w=1.0)
#         dim(init_vals$mu) <- 1
#         dim(init_vals$nu) <- 1
#         dim(init_vals$w) <- 1
#         }
#   # if(!(grepl(mix_ens,"EW",fixed = TRUE))){
#   #   init_vals[["omega_k"]] <- t(replicate(K, TLP_results_s2$params))
#   # }
#     if(!(grepl(mix_ens,"EW",fixed = TRUE)) && grepl("BMC1",mix_ens,fixed = TRUE)){
#     init_vals[["omega_k"]] <- t(replicate(K, TLP_results_s2$params))
#   } else if(!(grepl(mix_ens,"EW",fixed = TRUE)) && grepl("BMC2",mix_ens,fixed = TRUE)){
#     init_vals[["omega_k"]] <- t(replicate(K, TLP_results_s2$params))
#   } else if(!(grepl(mix_ens,"EW",fixed = TRUE)) && grepl("BMC3",mix_ens,fixed = TRUE)){
#     init_vals[["omega_k"]] <- t(matrix(c(BMC2_results_s2$params[5],
#                                          BMC2_results_s2$params[7],
#                                          BMC2_results_s2$params[9],
#                                          BMC2_results_s2$params[6],
#                                          BMC2_results_s2$params[8],
#                                          BMC2_results_s2$params[10],
#                                          TLP_results_s2$params),
#                                        nrow=ncol(comp_forecasts2),ncol=3))
#   } else if(!(grepl(mix_ens,"EW",fixed = TRUE)) && grepl("BMC4",mix_ens,fixed = TRUE)){
#     init_vals[["omega_k"]] <- t(matrix(c(BMC3_results_s2$params[7],
#                                          BMC3_results_s2$params[10],
#                                          BMC3_results_s2$params[13],
#                                          BMC3_results_s2$params[8],
#                                          BMC3_results_s2$params[11],
#                                          BMC3_results_s2$params[14],
#                                          BMC3_results_s2$params[9],
#                                          BMC3_results_s2$params[12],
#                                          BMC3_results_s2$params[15],
#                                          TLP_results_s2$params),
#                                        nrow=ncol(comp_forecasts2),ncol=4))
#   } else if(!(grepl(mix_ens,"EW",fixed = TRUE)) && grepl("BMC5",mix_ens,fixed = TRUE)){
#     init_vals[["omega_k"]] <- t(matrix(c(BMC4_results_s2$params[9],
#                                          BMC4_results_s2$params[13],
#                                          BMC4_results_s2$params[17],
#                                          BMC4_results_s2$params[10],
#                                          BMC4_results_s2$params[14],
#                                          BMC4_results_s2$params[18],
#                                          BMC4_results_s2$params[11],
#                                          BMC4_results_s2$params[15],
#                                          BMC4_results_s2$params[19],
#                                          BMC4_results_s2$params[12],
#                                          BMC4_results_s2$params[16],
#                                          BMC4_results_s2$params[20],
#                                          TLP_results_s2$params),
#                                        nrow=ncol(comp_forecasts2),ncol=5))
#   }
#   hyperpars <- list(rep(1.0,K),rep(1.0,ncol(comp_forecasts2)),rep(1/ncol(comp_forecasts2),ncol(comp_forecasts2)))
#   names(hyperpars) <- c("alpha_w","alpha_omega","omega_ew")
#   assign(paste0(mix_ens,"_results_s2"),
#          make_mix_ensemble(mix_ens,K,comp_forecasts2,comp_pits2, init_vals,hyperpars,ind_est, !ind_est))
#   }
```

```{r, include=FALSE}
# Evaluation ------------------------------------------------------------------
table2 <-make_table(forecast_names[c(1:4)],"s2",comp_forecasts2)
table21 <-make_table_bmc(forecast_names[5:12],"s2")
mls2 <- make_ls(forecast_names[1:12],"s2")
```

```{r, fig.align="center",message=FALSE,warning=FALSE,fig.cap=""}
# Overview over estimated parameters
knitr::kable(list(table2,table21[,1:5]), "latex", booktabs = T, 
             caption = "Model and Beta Mixing Weight Parameters",escape=FALSE) %>%
  kable_styling(font_size = 8, latex_options = "HOLD_position")
knitr::kable(table21[,6:15], "latex", booktabs = T,caption = "Mixture Parameters",escape=FALSE) %>%
  kable_styling(font_size = 8, latex_options = "HOLD_position")
knitr::kable(table21[,16:30], "latex", booktabs = T,caption = "Mixture Parameters",escape=FALSE) %>%
  kable_styling(font_size = 8, latex_options = "HOLD_position")
knitr::kable(list(mls2[1:4,],mls2[5:12,]), "latex", booktabs = T,caption = "Log Score",escape=FALSE) %>%
  kable_styling(font_size = 8, latex_options = "HOLD_position")
```

\clearpage

```{r,fig.align="center",fig.width=7, fig.height=11,message=FALSE,warning=FALSE,fig.cap=""}
# PIT Histogramme
plot_PITs(comp_pits2,forecast_names[1:12],"s2",train=TRUE)
```

\clearpage

```{r,fig.align="center",fig.width=7, fig.height=11,message=FALSE,warning=FALSE,fig.cap=""}
# PIT Histogramme
plot_PITs(comp_pits2,forecast_names[1:12],"s2",train=FALSE)
```

\clearpage

```{r,fig.align="center",fig.width=7, fig.height=11,message=FALSE,warning=FALSE,fig.cap=""}
# PDF
plot_PDFs(Y,comp_forecasts2,forecast_names[1:12],"s2",c(0,1.8))
```

